### 2015-11-04 CVPR16/Source/abstract.tex
Add Abstract"

\begin{abstract}
We propose a model for representation of objects so that points can be
probabilistically  associated to the tracklets while accounting for occlusion.
We compare our approach against state of the art motion segmentation methods.
\end{abstract}

>>>>

\begin{abstract}
This paper studies the problem of segmenting tracked feature points of multiple objects in a video sequence. We consider scenes that contain both dynamic and static objects which usually appear in the context of autonomous driving (e.g., moving and parked cars) and occlusions among objects. We propose a novel continuous model for representing objects so that point tracks can be probabilistically and accurately assigned to the corresponding object while accounting for object occlusions. Detailed experiments on the KITTI dataset show the superiority of the propose method over the baseline method which simply uses detection bounding boxes for resolving occlusions and other state-of-the-art motion segmentation methods which cannot cope well with static objects. As a notable application, we show how our continuous occlusion model benefits the task of 3D localization of traffic participants in autonomous driving.  
\end{abstract}

### 2015-11-04 CVPR16/Source/intro.tex
Add Abstract"

\section{Introduction}
The problem of segmenting points to objects often comes up in different
computer vision problems especially in multi-body 
reconstruction and localization. Given correspondence points on
consecutive frames, the problem becomes one of finding out which points belong
to which object, following which one can use the consensus of segmented points
to reconstruct or localize the object more accurately. Without additional 
information, this is a very difficult problem as attempted by semantic segmentation 
and motion segmentation methods. However, in the problems like reconstruction and
localization one can use the hypothesis of the algorithm as the feedback.
% What is the problem we are trying to solve, and why is it even important?

>>>>

\section{Introduction}
Motion segmentation is a fundamental problem in computer vision, which aims to separate the motions of multiple objects appearing in a video sequence. The input data is usually a set of points extracted on the surfaces of the objects, which are then tracked through the video sequence. Motion segmentation serves as an important preprocessing step for different applications such as 3D localization and reconstruction, where the point tracks associated with each individual object can be used to localize or reconstruct the object in the 3D space accurately.

Previous work 
Input assumption
Contributions

The problem of segmenting points to objects often comes up in different
computer vision problems especially in multi-body 
reconstruction and localization. Given correspondence points on
consecutive frames, the problem becomes one of finding out which points belong
to which object, following which one can use the consensus of segmented points
to reconstruct or localize the object more accurately. Without additional 
information, this is a very difficult problem as attempted by semantic segmentation 
and motion segmentation methods. However, in the problems like reconstruction and
localization one can use the hypothesis of the algorithm as the feedback.
% What is the problem we are trying to solve, and why is it even important?
